### 2019-09-09 ThesisJo/3_publications.tex
2019-09-08

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three reconstruct from echoes and the last synthesizes through simulation.

@@

This article evaluates time domain MVDR on GPUs for use in active sonar imaging. We refer to MVDR as fully adaptive because it computes array weights analytically from spatial features of the data, yielding a continuous solution space. Like any data-driven algorithm, it requires statistically distinguishable signal and noise. However, in typical active systems, the signal is highly correlated with the noise and has poor temporal sample support. Therefore, in its unconstrained form, MVDR overfits the data, yields high variance and fails to generate representative images.

@@

>>>>

We present four journal published papers concerned with \emph{adaptive} and \emph{hardware accelerated} formation of acoustic images: the first three through \emph{reconstruct} from echoes and the last \emph{synthesizes} through simulation.

@@

This article accelerates time-domain MVDR with GPUs for use in active sonar imaging. Time-domain MVDR is the reference method for creating sonar images using the minimum variance optimization, aimed at reducing noise and interference while preserving signal integrity while. We refer to it as fully adaptive because it computes array weights analytically from spatial features of the data, yielding array weights from a continuous solution space that are optimal in the minimum variance sense. Like any data-driven algorithm, it requires statistically distinguishable signal and noise. However, in typical active systems, the signal is highly correlated with the noise and has poor temporal sample support. Therefore, in its unconstrained form, MVDR overfits the data, yields high variance and fails to generate representative images.

@@

%Time-domain MVDR is the reference method for creating sonar images using the minimum variance criterion. It computes array weights analytically, yielding optimal weights in the minimum variance sense. Initially, this may seem ideal, but its use is cumbersome: parameters for temporal averaging, spatial averaging and regularization must often be fine-tuned ad-hoc to obtain improved image quality. GPU acceleration mitigates the high computational complexity resulting from estimating and inverting a spatial covariance matrix, yielding real-time performance.
